SDR enhancement by clouds

### 2024-03-15 article/article.Rmd
Commit 2024-03-15 09:10

Our dataset after the proccesing consists of

total data points `r ST_total$wattGLB.N`

of which CE are `r ST_total$GLB_diff.N_pos`

and `r ST_extreme_total$GLB_diff.N_pos` are ECE

@@

ST_extreme_total

>>>>

Our dataset, after the data selection processing, consists of
`r ST_total$wattGLB.N` records of GHI, of which  
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\%$ are CE and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\%$ are ECE.
The stronger highest

@@

ST_daily[max(wattGLB.max,na.rm = T), ]

ST_daily[max(GLB_diff.max,na.rm = T), ]
